---
title: "final_project"
author: "Vivian Zhang"
date: "2/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(readxl)
library(janitor)
library(rvest)
library(magrittr)
library(base)
library(reshape2)
library(shiny)
# library(ggmap)
# library(mapproj)
# library(rworldmap)
# library(rworldxtra)
library(plotly)
library(leaflet)
library(tidyverse)

```

# Comments for Milestone 5

I worked quite a bit on my graphs this week. First, I cleaned my data because I noticed that after a few inner_join runs, some values (such as remittances in usd) remained static from 1980-2018. This was because I also needed to join columns by year, not just country name. I created a new column in my full_data dataframe that looks at the sum of remittances (in usd) in all EU member states in any given year from 1980 to 2018. Initially, the y axis showed what looked like scientific notation because the numbers were quite large and unwieldy. I play with scale_y_continuous to make it clearer. I decided to add both geom_line and geom_plot, so as to allow the user to hover over specific discrete points as well as see the overall trend of the data. In order to allow the hover feature to work, I learned more about the shiny toolkit. I spent some time experimenting with maps. At first, I tried a Google Maps API key, but after looking through more past projects, I decided to use leaflet. I figured out how to zoom into Europe specifically. Then, I experimented with the Shiny slider that allowed the user to select the year. I am currently working on addPolygons and trying to figure out which data input I need to create a choropleth map for remittances in usd. I will need to read more about spatial data in order to do so - somehow, I will need to communicate the country names as coordinates, so that I can match countries on the map with the country names I have in my full_data dataset. I already noticed that the countries are named differently between the leaflet map and my dataset. I am happy with the progress I have made so far; I spent quite a bit of time reading about leaflet and how to map my data, so hopefully the mapping won't be too difficult.


```{r member states}

eumemberinfo <- read_html('https://en.wikipedia.org/wiki/Member_state_of_the_European_Union', skip = 0)

eumemberinfo <- eumemberinfo %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[5]') %>%
  html_table()

eumemberinfo <- eumemberinfo[[1]]

# Removing Wikipedia annotations

eumemberinfo$Name <- str_remove_all(eumemberinfo$Name, "\\[.*\\]")

# Changing the names because Eastern European countries are labeled
# differently on the two datasets

eumemberinfo$Name[eumemberinfo$Name == "Czechia"] <- "Czech Republic"

eumemberinfo$Name[eumemberinfo$Name == "Slovakia"] <- "Slovak Republic"

name <- eumemberinfo %>% 
  select(Name) 

names(name) <- c("sender")
  
```

```{r dataset, include=FALSE}

# Load remittances in USD in a given country, in alphabetical order

usd <- read_excel("data/remittances_usd.xls", skip = 3)

# Trying to get rid of the x in front of the data
# Filter to only show between 1980 to present
# Repeatedly getting the error that argument "pattern" is missing, with no
# default
# Convert USD to Euros - maybe later

usd <- usd %>%
  pivot_longer(
    cols = `1980`:`2018`,
    names_to = "year",
    names_prefix = "yr"
               )

usd <- usd[,-c(5:25)]

# join this with the eumemberinfo to only look at member states

full_data <- usd %>%
  inner_join(eumemberinfo, by = c("Country Name" = "Name")) %>%
  rename(remittances_in_usd = value) %>%
  clean_names %>%
  filter(country_name %in% name$sender)

# Load remittances as percentage of GDP for a given country

percent_gdp <- read_excel("data/remittance_percentgdp.xls", skip = 3)

percent_gdp <- percent_gdp %>%
  pivot_longer(
    cols = `1980`:`2018`,
    names_to = "year",
    names_prefix = "yr") %>%
  rename(remittances_percent_gdp = value) %>%
  clean_names %>%
  filter(country_name %in% name$sender)

percent_gdp <- percent_gdp[,-c(5:25)]

# Join this with the previous data and select only the relevant columns

full_data <- full_data %>%
  inner_join(percent_gdp, by = c("country_name"="country_name", "year"="year"), suffix = c("_usd", "_gdp")) %>%
  select(country_name, country_code_usd, accession, year, remittances_in_usd, remittances_percent_gdp)

```

```{r remittance inflows}

# Load remittance inflows

remittance_inflows <- read_excel("data/remittance_inflows.xlsx", skip = 0)

# Pivot years into column, clean names, rename columns
# Filter for EU countries, remove columns

remittance_inflows <- remittance_inflows %>%
  pivot_longer(
    cols = `1980`:`2018`,
    names_to = "remittance_inflows",
    names_prefix = "yr") %>%
  clean_names %>%
  rename(remmitance_inflows=value, year=remittance_inflows, country_name = migrant_remittance_inflows_us_million) %>%
  filter(country_name %in% name$sender) %>%
  select(-c(x2019e, remittances_as_a_share_of_gdp_in_2019_percent))

# Join into full dataset

full_data <- full_data %>%
  inner_join(remittance_inflows, by = c("country_name"="country_name", "year"="year"))

# <- data[ -c(19:22) ] %>%
# na.omit()

```

```{r plot}

# Get my data from full_data
# Add a new column called sum_remittance_usd
# ungroup and cast year into a numeric

mydata <- full_data %>%
  na.omit %>%
  group_by(year) %>%
  summarize(sum_remittance_usd = sum(remittances_in_usd)) %>%
  ungroup() %>%
  mutate(year = as.numeric(as.character(year)))

```


```{r bilateral remittance 2010}

brf_2010 <- read_excel("data/BilateralRemittanceMatrix2010.xlsx", skip = 1) %>% 
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2010)

names(brf_2010) <- c("sender", "recipient", "amount", "year") 

brf_2010 <- inner_join(name, brf_2010, by = "sender")

```

```{r bilateral remittance 2011}

brf_2011 <- read_excel("data/BilateralRemittanceMatrix2011.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2011)

names(brf_2011) <- c("sender", "recipient", "amount", "year") 

brf_2011 <- inner_join(name, brf_2011, by = "sender")

```

```{r bilateral remittance 2012}

brf_2012 <- read_excel("data/BilateralRemittanceMatrix2012.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2012)

names(brf_2012) <- c("sender", "recipient", "amount", "year") 

brf_2012 <- inner_join(name, brf_2012, by = "sender")

```

```{r bilateral remittance 2013}

brf_2013 <- read_excel("data/BilateralRemittanceMatrix2013.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2013)

names(brf_2013) <- c("sender", "recipient", "amount", "year") 

brf_2013 <- inner_join(name, brf_2013, by = "sender")

```


```{r bilateral remittance 2014}

brf_2014 <- read_excel("data/BilateralRemittanceMatrix2014.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2014)

names(brf_2014) <- c("sender", "recipient", "amount", "year") 

brf_2014 <- inner_join(name, brf_2014, by = "sender")

```

```{r bilateral remittance 2015}

brf_2015 <- read_excel("data/BilateralRemittanceMatrix2015.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2015)

names(brf_2015) <- c("sender", "recipient", "amount", "year") 

brf_2015 <- inner_join(name, brf_2015, by = "sender")

```

```{r bilateral remittance 2016}

brf_2016 <- read_excel("data/bilateralremittancematrix2016.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2016)

names(brf_2016) <- c("sender", "recipient", "amount", "year") 

brf_2016 <- inner_join(name, brf_2016, by = "sender")

```

```{r bilateral remittance 2017}

brf_2017 <- read_excel("data/bilateralremittancematrix2017.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2017)

names(brf_2017) <- c("sender", "recipient", "amount", "year") 

brf_2017 <- inner_join(name, brf_2017, by = "sender")

```

```{r join data}
# Filter for only EU member states
# Clean data so we don't have so many 0.0000000e's and have 0's instead
# Current columns are remittance-receiving countries
# IMPORTANT: How do I get the 2012 label to show up
# Is there a less redundant way to do this
# Finally is to flip the axis the other way, so I can see when
# EU members are senders

# mytempdata <- inner_join(brf_2010, brf_2011, by = "sender", suffix = c("_2010", "_2011"))
# 
# mytempdata <- inner_join(mytempdata, brf_2012, by = "sender", suffix = c("_2011", "_2012"))

```

```{r rbind}

# all_bilateral_remittance <- rbind(brf_2010, brf_2011, brf_2012)

```

```{r map plot}

# # All data loaded. Next, map showing the remittances in USD.

# Using Leaflet, an open-source Javascript library
# to create an interactive map

# Creating shiny slider going from 1980-2018

# ui = fluidPage(
#   sliderInput(inputId = "year", "Year", 1980, 2018, value = 2010), leafletOutput(outputId = "map")
# )

# Creating a function with our maps
# inputs and outputs
# Put into the shinyApp function

# This is the shinyApp setup (including the server function) that I will
# be working with

# server = function(input, output) {
  # output$map = renderLeaflet({
  #   leaflet() })
#       addPolygons(data = full_data, fillcolor = ~qpal(full_data$remittances_in_usd)) %>%
#       addTiles() %>%
#       setView(30,55,3)
#   })
# }

# shinyApp(ui, server)

# Color palette defined

# qpal <- colorNumeric(palette = "Blues", domain = full_data$remittances_in_usd)

# Generating the map of Europe with colors

euromap <- leaflet() %>%
  addTiles() %>%
  setView(30, 55, 3)

euromap

#   addPolygons(data = full_data, stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1, color = ~qpal(remittances_in_usd))

# addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1, color = ~qpal(full_data$remittances_in_usd)) %>%
# qpal <- colorQuantile("Blues", full_data$remittances_in_usd)

```

