---
title: "final_project"
author: "Vivian Zhang"
date: "2/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(janitor)
library(rvest)
library(magrittr)
library(base)
library(reshape2)
library(tidyverse)

```

```{r member states}

eu_members <- read_html('https://en.wikipedia.org/wiki/Member_state_of_the_European_Union', skip = 0)

eumemberinfo <- eu_members %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[5]') %>%
  html_table()

eumemberinfo <- eumemberinfo[[1]]

# Removing Wikipedia annotations

eumemberinfo$Name <- str_remove_all(eumemberinfo$Name, "\\[.*\\]")

# Changing the names because Eastern European countries are labeled
# differently on the two datasets

eumemberinfo$Name[eumemberinfo$Name == "Czechia"] <- "Czech Republic"

eumemberinfo$Name[eumemberinfo$Name == "Slovakia"] <- "Slovak Republic"

name <- eumemberinfo %>% 
  select(Name) 

names(name) <- c("sender")

name_country <- eumemberinfo %>% 
  select(Name) 

names(name_country) <- c("country_name")
  
```

```{r dataset, include=FALSE}

# Load remittances in USD in a given country, in alphabetical order

usd <- read_excel("data/remittances_usd.xls", skip = 3) %>%
  select(-c("Indicator Name", "Indicator Code", "Country Code")) %>%
  melt(id.vars = "Country Name") %>%
  mutate(year = as.numeric(variable) + 1959) %>%
  filter(year >= 1980) %>%
  clean_names() %>%
  select(-c(variable)) %>%
  drop_na()

usd <- inner_join(name_country, usd, by = "country_name")

names(usd) <- c("country", "remittances_in_usd", "year")
# full_data <- usd %>%
#   inner_join(eumemberinfo, by = c("country_name" = "Name"))

# Load remittances as percentage of GDP for a given country

percent_gdp <- read_excel("data/remittance_percentgdp.xls", skip = 3) %>%
  clean_names()

# percent_gdp <- percent_gdp %>%
#   pivot_longer(
#     cols = starts_with("x"),
#     names_to = "year",
#     names_prefix = "yr"
#                )

# Join this with the previous data and select only the relevant columns

full_data <- full_data %>%
  inner_join(percent_gdp, by = "country_name", suffix = c("_usd", "_gdp")) %>%
  select(country_name, country_code_gdp, starts_with("x"))

# full_data <- sub("^[^1|2]+\\.", "", full_data)

# full_data <- substr(paris$ratification, 0, 4)

```

```{r remittance inflows}

remittance_inflows <- read_excel("data/remittance_inflows.xlsx", skip = 0) %>%
  clean_names()

full_data <- full_data %>%
  inner_join(remittance_inflows, by = c("country_name" = "migrant_remittance_inflows_us_million"))

# <- data[ -c(19:22) ] %>%
# na.omit()

```

```{r bilateral remittance 2010}

brf_2010 <- read_excel("data/BilateralRemittanceMatrix2010.xlsx", skip = 1) %>% 
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2010)

names(brf_2010) <- c("sender", "recipient", "amount", "year") 

brf_2010 <- inner_join(name, brf_2010, by = "sender")

```

```{r bilateral remittance 2011}

brf_2011 <- read_excel("data/BilateralRemittanceMatrix2011.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2011)

names(brf_2011) <- c("sender", "recipient", "amount", "year") 

brf_2011 <- inner_join(name, brf_2011, by = "sender")

```

```{r bilateral remittance 2012}

brf_2012 <- read_excel("data/BilateralRemittanceMatrix2012.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2012)

names(brf_2012) <- c("sender", "recipient", "amount", "year") 

brf_2012 <- inner_join(name, brf_2012, by = "sender")

```

```{r bilateral remittance 2013}

brf_2013 <- read_excel("data/BilateralRemittanceMatrix2013.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2013)

names(brf_2013) <- c("sender", "recipient", "amount", "year") 

brf_2013 <- inner_join(name, brf_2013, by = "sender")

```


```{r bilateral remittance 2014}

brf_2014 <- read_excel("data/BilateralRemittanceMatrix2014.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2014)

names(brf_2014) <- c("sender", "recipient", "amount", "year") 

brf_2014 <- inner_join(name, brf_2014, by = "sender")

```

```{r bilateral remittance 2015}

brf_2015 <- read_excel("data/BilateralRemittanceMatrix2014.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2015)

names(brf_2015) <- c("sender", "recipient", "amount", "year") 

brf_2015 <- inner_join(name, brf_2015, by = "sender")

```

```{r bilateral remittance 2016}

brf_2016 <- read_excel("data/bilateralremittancematrix2016.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2016)

names(brf_2016) <- c("sender", "recipient", "amount", "year") 

brf_2016 <- inner_join(name, brf_2016, by = "sender")

```

```{r bilateral remittance 2017}

brf_2017 <- read_excel("data/bilateralremittancematrix2017.xlsx", skip = 1) %>%
  melt(id.vars = "Remittance-receiving country (across)                                                              -                                                 Remittance-sending country (down)") %>%
  mutate(year = 2017)

names(brf_2017) <- c("sender", "recipient", "amount", "year") 

brf_2017 <- inner_join(name, brf_2017, by = "sender")

```

# Filter for only EU member states
# Clean data so we don't have so many 0.0000000e's and have 0's instead
# Current columns are remittance-receiving countries
# IMPORTANT: How do I get the 2012 label to show up
# Is there a less redundant way to do this
# Finally is to flip the axis the other way, so I can see when
# EU members are senders

mytempdata <- inner_join(brf_2010, brf_2011, by = "remittance_receiving_country_across_remittance_sending_country_down", suffix = c("_2010", "_2011"))

mytempdata <- inner_join(mytempdata, brf_2012, by = "remittance_receiving_country_across_remittance_sending_country_down", suffix = c("_2011", "_2012"))

mytempdata = merge(mytempdata, mydata3)

# full_data <- usd %>%
#   inner_join(eumemberinfo, by = c("country_name" = "Name"))


```

```{r rbind}
all_bilateral_remittance <- rbind(brf_2010, brf_2011, brf_2012)
```



